Is an automatic or manual transmission better for MPG ?
========================================================

In this study, we are paricularly interested in answering the two questions below

* Is an automatic or manual transmission better for miles/(US) gallon (MPG) ?
* Quantifying how different is the MPG between automatic and manual transmissions?

Our dataset `mtcars` contains **`r nrow(mtcars)`** observations on  the following **`r ncol(mtcars)`** variables.
* [, 1]  `mpg`	 Miles/(US) gallon
* [, 2]	 `cyl`	 Number of cylinders
* [, 3]	 `disp`	 Displacement (cu.in.)
* [, 4]	 `hp`	 Gross horsepower
* [, 5]	 `drat`	 Rear axle ratio
* [, 6]	 `wt`	 Weight (lb/1000)
* [, 7]	 `qsec`	 1/4 mile time
* [, 8]	 `vs`	 V/S
* [, 9]	 `am`	 Transmission (0 = automatic, 1 = manual)
* [,10]	 `gear`	 Number of forward gears
* [,11]	 `carb`	 Number of carburetors

```{r}
str(mtcars)
```
Let's first do a multivarible regression as following
```{r}
summary(lm(mpg ~ am, data = mtcars))$coefficients
```
Then we will use the **backward-elimination** strategy to eliminate the unrelated variables one-at-a-time. 


